Factors affecting inferences on natural mortality and associated environmental effects in state-space age-structured assessment models

### 2025-12-19 Ecov_study/mortality/manuscript/manuscript_R1.tex
revision for project 0 complete, save work for M-Ecov revision

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Factors affecting inferences on natural mortality and associated environmental effects in state-space age-structured assessment models},
  pdfauthor={Timothy J. Miller1,2; Gregory L. Britten3; Elizabeth N. Brooks2; Gavin Fay4; Alexander C. Hansell2; Christopher M. Legault2; Brandon Muffley5; John Wiedenmann6},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{url}
\usepackage{setspace}
%\singlespacing
%\onehalfspacing
\doublespacing
\usepackage{lineno}
\linenumbers
\usepackage[belowskip=0pt,aboveskip=0pt]{caption}
\usepackage{relsize}
\usepackage{float}
\usepackage{lscape}
\usepackage{longtable}
\usepackage{amsmath,rotating}
\usepackage[scanall]{psfrag}
\usepackage{bm}
\usepackage{caption,graphics}
\usepackage{graphicx}
\usepackage{sectsty}
\usepackage{color}
\usepackage{fancyhdr}
\usepackage{xspace}
\usepackage{textcomp}
\usepackage{upgreek}
\renewcommand\figurename{Fig.}
\captionsetup{labelsep=period, singlelinecheck=false}
\newcommand{\changesize}[1]{\fontsize{#1pt}{#1pt}\selectfont}
\renewcommand{\arraystretch}{1.5}
%\renewcommand\theadfont{}

\newcommand{\Fmsy}{\ensuremath{F_{\text{MSY}}}\xspace}
\newcommand{\Fspr}[1]{\ensuremath{F_{\text{{#1}\%}}}\xspace}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[round]{natbib}
\bibliographystyle{cjfas.bst}

\title{Factors affecting inferences on natural mortality and associated environmental effects in state-space age-structured assessment models}
\author{Timothy J. Miller\textsuperscript{1,2} \and Gregory L. Britten\textsuperscript{3} \and Elizabeth N. Brooks\textsuperscript{2} \and Gavin Fay\textsuperscript{4} \and Alexander C. Hansell\textsuperscript{2} \and Christopher M. Legault\textsuperscript{2} \and Brandon Muffley\textsuperscript{5} \and John Wiedenmann\textsuperscript{6}}
\date{18 June, 2025}

@@

\hypertarget{methods}{%
\section*{Methods}\label{methods}}
\addcontentsline{toc}{section}{Methods}

Our analyses used the Woods Hole Assessment Model (WHAM) to construct both OMs and EMs \citep{millerstock20, stockmiller21, milleretal_inreview}. The WHAM package has been used extensively to configure OMs and EMs for several other simulation studies \citep{stocketal21, legaultetal23, lietal24, brittenetal_inreview, lietal_inreview_a} and is used to assess many commercially important stocks in the Northeast U.S. \citep[e.g.,][]{nefsc22, nefsc22a, nefsc24}. We used \href{https://github.com/timjmiller/wham/tree/77bbd946e4881216a439933473d1c58b21c270c3}{version 1.0.6.9000, commit 77bbd94} to generate all results.

@@

For each simulated data set we fit a set of 12 estimating models (EMs). The factors that distinguish the estimating models, also described in detail below, include source of population process error type (3 levels) whether (median) \(M\) was estimated or assumed known (2 levels), and whether the effect of the environmental covariate on \(M\) was estimated or not (2 levels).

@@

\hypertarget{operating-models}{%
\subsection*{Operating models}\label{operating-models}}
\addcontentsline{toc}{subsection}{Operating models}

\hypertarget{environmental-covariate}{%
\subsubsection*{Environmental covariate}\label{environmental-covariate}}
\addcontentsline{toc}{subsubsection}{Environmental covariate}

@@

\hypertarget{population}{%
\subsubsection*{Population}\label{population}}
\addcontentsline{toc}{subsubsection}{Population}

@@

\hypertarget{catch-and-index-observations}{%
\subsubsection*{Catch and index observations}\label{catch-and-index-observations}}
\addcontentsline{toc}{subsubsection}{Catch and index observations}

@@

\hypertarget{estimating-models}{%
\subsection*{Estimating models}\label{estimating-models}}
\addcontentsline{toc}{subsection}{Estimating models}

@@

\hypertarget{performance-measures}{%
\subsection*{Performance measures}\label{performance-measures}}
\addcontentsline{toc}{subsection}{Performance measures}

\hypertarget{em-convergence}{%
\subsubsection*{EM convergence}\label{em-convergence}}
\addcontentsline{toc}{subsubsection}{EM convergence}

@@

\hypertarget{parameter-estimation}{%
\subsubsection*{Parameter estimation}\label{parameter-estimation}}
\addcontentsline{toc}{subsubsection}{Parameter estimation}

@@

\hypertarget{results}{%
\section*{Results}\label{results}}
\addcontentsline{toc}{section}{Results}

@@

\hypertarget{em-convergence-1}{%
\subsection*{EM Convergence}\label{em-convergence-1}}
\addcontentsline{toc}{subsection}{EM Convergence}

@@

\hypertarget{aic-performance}{%
\subsection*{AIC performance}\label{aic-performance}}
\addcontentsline{toc}{subsection}{AIC performance}

@@

\hypertarget{covariate-effect-estimation}{%
\subsection*{Covariate effect estimation}\label{covariate-effect-estimation}}
\addcontentsline{toc}{subsection}{Covariate effect estimation}

@@

\hypertarget{median-natural-mortality-rate-estimation}{%
\subsection*{Median natural mortality rate estimation}\label{median-natural-mortality-rate-estimation}}
\addcontentsline{toc}{subsection}{Median natural mortality rate estimation}

@@

\hypertarget{terminal-year-natural-morality-rate}{%
\subsection*{Terminal year natural morality rate}\label{terminal-year-natural-morality-rate}}
\addcontentsline{toc}{subsection}{Terminal year natural morality rate}

@@

\hypertarget{terminal-year-spawning-stock-biomass}{%
\subsection*{Terminal year spawning stock biomass}\label{terminal-year-spawning-stock-biomass}}
\addcontentsline{toc}{subsection}{Terminal year spawning stock biomass}

@@

\hypertarget{discussion}{%
\section*{Discussion}\label{discussion}}
\addcontentsline{toc}{section}{Discussion}

@@

\hypertarget{acknowledgements}{%
\section*{Acknowledgements}\label{acknowledgements}}
\addcontentsline{toc}{section}{Acknowledgements}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\end{CSLReferences}

@@

@@

\hypertarget{supplemental-materials}{%
\section*{Supplemental Materials}\label{supplemental-materials}}
\addcontentsline{toc}{section}{Supplemental Materials}

\hypertarget{convergence-results}{%
\subsection*{Convergence results}\label{convergence-results}}
\addcontentsline{toc}{subsection}{Convergence results}

@@

\hypertarget{aic-results}{%
\subsection*{AIC results}\label{aic-results}}
\addcontentsline{toc}{subsection}{AIC results}

@@

\hypertarget{covariate-effect-bias}{%
\subsection*{Covariate effect bias}\label{covariate-effect-bias}}
\addcontentsline{toc}{subsection}{Covariate effect bias}

@@

\hypertarget{covariate-effect-standard-error-estimation-bias}{%
\subsection*{Covariate effect standard error estimation bias}\label{covariate-effect-standard-error-estimation-bias}}
\addcontentsline{toc}{subsection}{Covariate effect standard error estimation bias}

@@

\hypertarget{covariate-effect-confidence-interval-coverage}{%
\subsection*{Covariate effect confidence interval coverage}\label{covariate-effect-confidence-interval-coverage}}
\addcontentsline{toc}{subsection}{Covariate effect confidence interval coverage}

@@

\hypertarget{covariate-effect-rmse}{%
\subsection*{Covariate effect RMSE}\label{covariate-effect-rmse}}
\addcontentsline{toc}{subsection}{Covariate effect RMSE}

@@

\hypertarget{covariate-effect-estimate-and-standard-error-example}{%
\subsection*{Covariate effect estimate and standard error example}\label{covariate-effect-estimate-and-standard-error-example}}
\addcontentsline{toc}{subsection}{Covariate effect estimate and standard error example}

@@

\hypertarget{median-natural-mortality-parameter-bias}{%
\subsection*{Median Natural mortality parameter bias}\label{median-natural-mortality-parameter-bias}}
\addcontentsline{toc}{subsection}{Median Natural mortality parameter bias}

@@

\hypertarget{median-natural-mortality-parameter-standard-error-estimation-bias}{%
\subsection*{Median natural mortality parameter standard error estimation bias}\label{median-natural-mortality-parameter-standard-error-estimation-bias}}
\addcontentsline{toc}{subsection}{Median natural mortality parameter standard error estimation bias}

@@

\hypertarget{median-natural-mortality-parameter-confidence-interval-coverage}{%
\subsection*{Median Natural mortality parameter confidence interval coverage}\label{median-natural-mortality-parameter-confidence-interval-coverage}}
\addcontentsline{toc}{subsection}{Median Natural mortality parameter confidence interval coverage}

@@

\hypertarget{median-natural-mortality-parameter-estimate-and-standard-error-example}{%
\subsection*{Median natural mortality parameter estimate and standard error example}\label{median-natural-mortality-parameter-estimate-and-standard-error-example}}
\addcontentsline{toc}{subsection}{Median natural mortality parameter estimate and standard error example}

@@

\hypertarget{median-natural-mortality-parameter-rmse}{%
\subsection*{Median Natural mortality parameter RMSE}\label{median-natural-mortality-parameter-rmse}}
\addcontentsline{toc}{subsection}{Median Natural mortality parameter RMSE}

@@

\hypertarget{terminal-year-natural-mortality-bias}{%
\subsection*{Terminal year natural mortality bias}\label{terminal-year-natural-mortality-bias}}
\addcontentsline{toc}{subsection}{Terminal year natural mortality bias}

@@

\hypertarget{terminal-year-natural-mortality-rmse}{%
\subsection*{Terminal year natural mortality RMSE}\label{terminal-year-natural-mortality-rmse}}
\addcontentsline{toc}{subsection}{Terminal year natural mortality RMSE}

@@

\hypertarget{terminal-year-spawning-stock-biomass-bias}{%
\subsection*{Terminal year spawning stock biomass bias}\label{terminal-year-spawning-stock-biomass-bias}}
\addcontentsline{toc}{subsection}{Terminal year spawning stock biomass bias}

@@

\hypertarget{terminal-year-spawning-stock-biomass-rmse}{%
\subsection*{Terminal year spawning stock biomass RMSE}\label{terminal-year-spawning-stock-biomass-rmse}}
\addcontentsline{toc}{subsection}{Terminal year spawning stock biomass RMSE}

@@

\hypertarget{terminal-year-fishing-mortality-bias}{%
\subsection*{Terminal year fishing mortality bias}\label{terminal-year-fishing-mortality-bias}}
\addcontentsline{toc}{subsection}{Terminal year fishing mortality bias}

@@

\hypertarget{terminal-year-fishing-mortality-rmse}{%
\subsection*{Terminal year fishing mortality RMSE}\label{terminal-year-fishing-mortality-rmse}}
\addcontentsline{toc}{subsection}{Terminal year fishing mortality RMSE}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\documentclass[
  12pt,
]{article}
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{5}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage[round]{natbib}
\bibliographystyle{cjfas.bst}
\usepackage{url}
\usepackage{setspace}
%\singlespacing
%\onehalfspacing
\doublespacing
\usepackage{lineno}
\linenumbers
\usepackage[belowskip=0pt,aboveskip=0pt]{caption}
\usepackage{relsize}
\usepackage{float}
\usepackage{lscape}
\usepackage{longtable}
\usepackage{amsmath,rotating}
\usepackage[scanall]{psfrag}
\usepackage{bm}
\usepackage{caption,graphics}
\usepackage{graphicx}
\usepackage{sectsty}
\usepackage{color}
\usepackage{fancyhdr}
\usepackage{xspace}
\usepackage{textcomp}
\usepackage{upgreek}
\renewcommand\figurename{Fig.}
\captionsetup{labelsep=period, singlelinecheck=false}
\newcommand{\changesize}[1]{\fontsize{#1pt}{#1pt}\selectfont}
\renewcommand{\arraystretch}{1.5}
%\renewcommand\theadfont{}

\newcommand{\Fmsy}{\ensuremath{F_{\text{MSY}}}\xspace}
\newcommand{\Fspr}[1]{\ensuremath{F_{\text{{#1}\%}}}\xspace}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Factors affecting inferences on natural mortality and associated environmental effects in state-space age-structured assessment models},
  pdfauthor={Timothy J. Miller1,2; Gregory L. Britten3; Elizabeth N. Brooks2; Gavin Fay4; Alexander C. Hansell2; Christopher M. Legault2; Brandon Muffley5; John Wiedenmann6},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Factors affecting inferences on natural mortality and associated environmental effects in state-space age-structured assessment models}
\author{Timothy J. Miller\textsuperscript{1,2} \and Gregory L. Britten\textsuperscript{3} \and Elizabeth N. Brooks\textsuperscript{2} \and Gavin Fay\textsuperscript{4} \and Alexander C. Hansell\textsuperscript{2} \and Christopher M. Legault\textsuperscript{2} \and Brandon Muffley\textsuperscript{5} \and John Wiedenmann\textsuperscript{6}}
\date{18 December, 2025}

@@

\section*{Methods}\label{methods}
\addcontentsline{toc}{section}{Methods}

Our analyses used the Woods Hole Assessment Model (WHAM) to construct both OMs and estimation models (EMs) \citep{millerstock20, stockmiller21, milleretal_inreview}. The WHAM package has been used extensively to configure OMs and EMs for several other simulation studies \citep{stocketal21, legaultetal23, lietal24, brittenetal_inreview, lietal_inreview_a} and is used to assess many commercially important stocks in the Northeast U.S. \citep[e.g.,][]{nefsc22, nefsc22a, nefsc24}. We used \href{https://github.com/timjmiller/wham/tree/77bbd946e4881216a439933473d1c58b21c270c3}{version 1.0.6.9000, commit 77bbd94} to generate all results.

@@

For each simulated data set we fit a set of 12 EMs. The factors that distinguish the estimating models, also described in detail below, include source of population process error type (3 levels) whether (median) \(M\) was estimated or assumed known (2 levels), and whether the effect of the environmental covariate on \(M\) was estimated or not (2 levels).

@@

\subsection*{Operating models}\label{operating-models}
\addcontentsline{toc}{subsection}{Operating models}

\subsubsection*{Environmental covariate}\label{environmental-covariate}
\addcontentsline{toc}{subsubsection}{Environmental covariate}

@@

\subsubsection*{Population}\label{population}
\addcontentsline{toc}{subsubsection}{Population}

@@

\subsubsection*{Catch and index observations}\label{catch-and-index-observations}
\addcontentsline{toc}{subsubsection}{Catch and index observations}

@@

\subsection*{Estimating models}\label{estimating-models}
\addcontentsline{toc}{subsection}{Estimating models}

@@

\subsection*{Performance measures}\label{performance-measures}
\addcontentsline{toc}{subsection}{Performance measures}

\subsubsection*{EM convergence}\label{em-convergence}
\addcontentsline{toc}{subsubsection}{EM convergence}

@@

\subsubsection*{Parameter estimation}\label{parameter-estimation}
\addcontentsline{toc}{subsubsection}{Parameter estimation}

@@

\section*{Results}\label{results}
\addcontentsline{toc}{section}{Results}

@@

\subsection*{EM Convergence}\label{em-convergence-1}
\addcontentsline{toc}{subsection}{EM Convergence}

@@

\subsection*{AIC performance}\label{aic-performance}
\addcontentsline{toc}{subsection}{AIC performance}

@@

\subsection*{Covariate effect estimation}\label{covariate-effect-estimation}
\addcontentsline{toc}{subsection}{Covariate effect estimation}

@@

\subsection*{Median natural mortality rate estimation}\label{median-natural-mortality-rate-estimation}
\addcontentsline{toc}{subsection}{Median natural mortality rate estimation}

@@

\subsection*{Terminal year natural morality rate}\label{terminal-year-natural-morality-rate}
\addcontentsline{toc}{subsection}{Terminal year natural morality rate}

@@

\subsection*{Terminal year spawning stock biomass}\label{terminal-year-spawning-stock-biomass}
\addcontentsline{toc}{subsection}{Terminal year spawning stock biomass}

@@

\section*{Discussion}\label{discussion}
\addcontentsline{toc}{section}{Discussion}

@@

\section*{Acknowledgements}\label{acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}

@@

@@

\begin{landscape}
\begin{figure}
\begin{center}
\includegraphics[width = 1.4\textwidth]{convergence_classification_plots}
\end{center}
\caption{Classification trees indicating primary factors determining convergence as defined by providing Hessian-based standard errors for R, R+S, and R+M OMs. Nodes denote percent convergence (top) and number of fits (bottom)  for the corresponding subset. Lower or higher convergence rates are indicated by more red or green polygons, respectively}\label{conv_class}
\end{figure}
\end{landscape}

\begin{table}
\caption{For each OM process error source (columns), percent reduction in deviance for logistic regression models fit to indicators of convergence (providing Hessian-based standard errors) with each OM and EM factor (rows) included individually, combined, and with second and third order interactions.}\label{convergence_PRD_table}
{\input{convergence_PRD_table}}
\end{table}

\begin{table}
\caption{For each OM process error source (columns), percent reduction in deviance for linear regression models fit to errors in estimation measured by Eq. \ref{bias_regression_response} for the median natural mortality rate parameter with each OM and EM factor (rows) included individually, combined, and with second and third order interactions.}\label{bias_median_M_converged_PRD_table}
{\input{bias_mean_M_converged_PRD_table}}
\end{table}

\begin{table}
\caption{For each OM process error source (columns), percent reduction in deviance for linear regression models fit to errors in estimation measured by Eq. \ref{bias_regression_response} for the the standard error of the MLE for median natural mortality rate with each OM and EM factor (rows) included individually, combined, and with second and third order interactions.}\label{bias_median_M_se_PRD_table}
{\input{bias_mean_M_se_PRD_table}}
\end{table}

\begin{table}
\caption{For each OM process error source (columns), percent reduction in deviance for linear regression models fit to errors in estimation measured by Eq. \ref{bias_regression_response} for the covariate effect on natural mortality ($\beta_E$) with each OM and EM factor (rows) included individually, combined, and with second and third order interactions.}\label{bias_ecov_beta_converged_PRD_table}
{\input{bias_ecov_beta_converged_PRD_table}}
\end{table}

\begin{table}
\caption{For each OM process error source (columns), percent reduction in deviance for linear regression models fit to errors in estimation measured by Eq. \ref{bias_regression_response} for the terminal year SSB with each OM and EM factor (rows) included individually, combined, and with second and third order interactions.}\label{bias_SSB_PRD_table}
{\input{bias_SSB_PRD_table}}
\end{table}

\begin{table}
\caption{For each OM process error source (columns), percent reduction in deviance for linear regression models fit to errors in estimation measured by Eq. \ref{bias_regression_response} for the median natural mortality rate parameter with each OM and EM factor (rows) included individually, combined, and with second and third order interactions.}\label{bias_median_M_complete_PRD_table}
{\input{bias_mean_M_complete_PRD_table}}
\end{table}

\begin{table}
\caption{For each OM process error source (columns), percent reduction in deviance for linear regression models fit to errors in estimation measured by Eq. \ref{bias_regression_response} for the covariate effect on natural mortality ($\beta_E$) with each OM and EM factor (rows) included individually, combined, and with second and third order interactions.}\label{bias_ecov_beta_complete_PRD_table}
{\input{bias_ecov_beta_complete_PRD_table}}
\end{table}

\section*{Supplemental Materials}\label{supplemental-materials}
\addcontentsline{toc}{section}{Supplemental Materials}

@@

\subsection*{Convergence results}\label{convergence-results}
\addcontentsline{toc}{subsection}{Convergence results}

@@

\subsection*{AIC results}\label{aic-results}
\addcontentsline{toc}{subsection}{AIC results}

@@

\subsection*{Covariate effect bias}\label{covariate-effect-bias}
\addcontentsline{toc}{subsection}{Covariate effect bias}

@@

\subsection*{Covariate effect standard error estimation bias}\label{covariate-effect-standard-error-estimation-bias}
\addcontentsline{toc}{subsection}{Covariate effect standard error estimation bias}

@@

\subsection*{Covariate effect confidence interval coverage}\label{covariate-effect-confidence-interval-coverage}
\addcontentsline{toc}{subsection}{Covariate effect confidence interval coverage}

@@

\subsection*{Covariate effect RMSE}\label{covariate-effect-rmse}
\addcontentsline{toc}{subsection}{Covariate effect RMSE}

@@

\subsection*{Covariate effect estimate and standard error example}\label{covariate-effect-estimate-and-standard-error-example}
\addcontentsline{toc}{subsection}{Covariate effect estimate and standard error example}

@@

\subsection*{Median Natural mortality parameter bias}\label{median-natural-mortality-parameter-bias}
\addcontentsline{toc}{subsection}{Median Natural mortality parameter bias}

@@

\subsection*{Median natural mortality parameter standard error estimation bias}\label{median-natural-mortality-parameter-standard-error-estimation-bias}
\addcontentsline{toc}{subsection}{Median natural mortality parameter standard error estimation bias}

@@

\subsection*{Median Natural mortality parameter confidence interval coverage}\label{median-natural-mortality-parameter-confidence-interval-coverage}
\addcontentsline{toc}{subsection}{Median Natural mortality parameter confidence interval coverage}

@@

\subsection*{Median natural mortality parameter estimate and standard error example}\label{median-natural-mortality-parameter-estimate-and-standard-error-example}
\addcontentsline{toc}{subsection}{Median natural mortality parameter estimate and standard error example}

@@

\subsection*{Median Natural mortality parameter RMSE}\label{median-natural-mortality-parameter-rmse}
\addcontentsline{toc}{subsection}{Median Natural mortality parameter RMSE}

@@

\subsection*{Terminal year natural mortality bias}\label{terminal-year-natural-mortality-bias}
\addcontentsline{toc}{subsection}{Terminal year natural mortality bias}

@@

\subsection*{Terminal year natural mortality RMSE}\label{terminal-year-natural-mortality-rmse}
\addcontentsline{toc}{subsection}{Terminal year natural mortality RMSE}

@@

\subsection*{Terminal year spawning stock biomass bias}\label{terminal-year-spawning-stock-biomass-bias}
\addcontentsline{toc}{subsection}{Terminal year spawning stock biomass bias}

@@

\subsection*{Terminal year spawning stock biomass RMSE}\label{terminal-year-spawning-stock-biomass-rmse}
\addcontentsline{toc}{subsection}{Terminal year spawning stock biomass RMSE}

@@

\subsection*{Terminal year fishing mortality bias}\label{terminal-year-fishing-mortality-bias}
\addcontentsline{toc}{subsection}{Terminal year fishing mortality bias}

@@

\subsection*{Terminal year fishing mortality RMSE}\label{terminal-year-fishing-mortality-rmse}
\addcontentsline{toc}{subsection}{Terminal year fishing mortality RMSE}
